Language Skills in an Ethnically Segmented Labour market: Estonia 1989 -- 2012

### 2018-07-24 paper/ijm.tex
Added file which compares original and revised file. This file will have to be submitted in the end. Produced by latexdiff and manual adjustments.

\fxsetup{theme=color}
%Custom commands
\newcommand{\eur}{\EUR}
\newcommand{\std}[1]{\emph{(#1)}}
\newcommand{\V}{\ensuremath\checkmark}
\def\fns{\footnotesize}
\renewcommand*{\vec}[1]{\boldsymbol{#1}}

\def\tenpc{$^{\ast}$}
\def\fivepc{$^{\ast\ast}$}
\def\onepc{$^{\ast\ast\ast}$}
\newcommand{\legend}{\normalsize{Significance levels:\hspace{1em} \tenpc : 10\% \hspace{1em} \fivepc : 5\% \hspace{1em} \onepc : 1\% \normalsize}}
\def\sep{0.5em}
\def\legendTwo{\multicolumn{3}{l}{\footnotesize{Significance levels
			:\hspace{1em} $\dag$ : 10\% \hspace{1em}
			$\ast$ : 5\% \hspace{1em} $\ast\ast$ : 1\% \normalsize}}}
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi} % needed for the tables produced by the esttab command in Stata, to avoid redundancy put here instead of in appendix.tex, where it is needed		
%SKB: Added for documenting the tables and figures
\newcommand{\modelTwo}{age, age\textsuperscript{2}, education, marriage, number of children, inter-ethnic household}
\newcommand{\modelThree}{\modelTwo, industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}
\newcommand{\modelThreeAdd}{industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}	
\newcommand{\restrictions}{The sample period is from year 2000 to year 2012. Sample is limited to persons
	25-55

 year old.}
\newcommand{\agerestrictions}{25-55 year olds only.}
% Modified section numbering: removed dot at the end as this jumps
% into the cross-references.
\renewcommand{\thesection}{\arabic{section}}
\renewcommand{\thesubsection}{\thesection.\arabic{subsection}}

@@

%\maketitle
%\begin{center}
%	\textbf{{\large Language Skills in an Ethnically Segmented Labour market:
%				Estonia 1989 -- 2012}} \\
%	{\large Sven-Kristjan Bormann} \\
%	\emph{School of Economics and Business Administration, University of Tartu, Narva mnt. 4, 51007 Tartu, Estonia\\ Tel.: +372 5844 3873\\ Email: \href{mailto:bormann@ut.ee}{bormann@ut.ee}}	\\
%
%	{\large Svetlana Ridala} \\
%	\emph{School of Business and Governance, Tallinn University of Technology, Akadeemia tee 3, 12618 Tallinn, Estonia\\ Email: \href{
%			mailto:svetlana.ridala@gmail.com}{
%			svetlana.ridala@gmail.com}} \\
%		{\large Ott Toomet}\\
%		\emph{Information School, University of Washington, USA; Email: \href{mailto:otoomet@uw.edu}{otoomet@uw.edu}}
%%	\emph{(Received XX XXXX 20XX; accepted XX XXXX 20XX)}\\
%	\textbf{Corresponding author:} Sven-Kristjan Bormann Email: \href{mailto:bormann@ut.ee}{bormann@ut.ee}
%\end{center}
%\paragraph{Short biographical note:} \hspace{0pt} \\
%Sven-Kristjan Bormann born 28.11.1985, graduated in 2011 from Kiel University, Germany in Economics with specialisation in Quantitative Economics and Computer Science. Since September 2012 PhD-student in Economics at Tartu University, Estonia. \\
%Svetlana Ridala born 28.03.1976, graduated in 2003 from Tallinn Pedagogical University, Estonia master's (scien) degree in mathematics. Since 2009 PhD-student in Economics at Tallinn School of Economics and Business Administration, Estonia.
%\\
%Ott-Siim Toomet born 18.03.1970, graduated in 2004 from Aarhus University, Denmark PhD in Economics. Since 2015 Visiting scholar, Information School, University of Washington.
%
%\paragraph{Research funding}
%This research was supported by European Social Fund's Doctoral Studies
%and Internationalisation Program DoRa through Archimedes Foundation, and the Estonian Science Foundation grant 8627.
%\newpage
%\noindent
{\centering \textbf{Language Skills in an Ethnically Segmented Labour market: Estonia 1989 -- 2012}}
\begin{abstract}
 \noindent
 \textbf{Purpose --} We analyse the relationship between skills of
 Estonian, Russian and English, and labour market
 outcomes in Estonia, a linguistically divided country.
 \\
 \textbf{Design/methodology/approach --} We use the Estonian Labour
 Force Surveys 1992--2012. We rely on multivariate linear regression
 models to document the relationship between language skills and
 labour market outcomes.
 \\
 \textbf{Findings --} Estonian language knowledge (for ethnic Russians)
 are important determinants of unemployment. Wage, in contrary, is
 closely related to English skills. Ethnic Russian men do not earn
 any premium from speaking Estonian, while women, fluent in Estonian
 earn approximately 10\% more. For ethnic Estonians, Russian fluency
 is associated with a similar income gain.
 \\
 \textbf{Research limitations/implications -- } Due to the
 observational nature of the data, the effects reported in our study
 are not causal effects. As a second limitation, the self-reported
 language skills data may be imprecise and hence the effects we
 report may be too small.
 \\
 \textbf{Practical implications --} Our results stress the role of
 workplace segregation, both along gender and ethnic lines, in
 determining the individual labour market experience. 
 \\
 \textbf{Originality/value --} We provide a comprehensive overview of
 the effects of language skills in a rapidly developing labour
 market in a linguistically divided economy. We analyse several
 languages with different legal status and document long-term
 trends in the effects.
 \\
\end{abstract}
\textbf{Keywords:} language skills, ethnicity, wage gap, unemployment, Estonia \\
\textbf{JEL classification:} J15, J31, J71

@@

We estimate three models that differ in terms of the control variables. The first specification only includes the language skills
and year dummies. It describes the ``raw'' effect of language skills,
net of strong time trends in our data.
The second specification additionally includes individual
characteristics (age, education) and family descriptors (marital
status, an indicator for inter-ethnic marriage, having kids up to 17 years
old) and county of residence. 
Finally, the third specification also adds industry, occupation, and other
workplace descriptors.
Note that in case of unemployment probability,
we only estimate the first two models.

@@

\begin{table}[h]
	\begin{center}
		\caption{Estimation results for unemployment.}
		\label{tab:unemployment_estimation_by_sex_and_ethnic_same_sample} %SKB 04.07.2018 14:22:Not yet updated only prepared
		\begin{tabular}{l D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad\qquad}
				D{.}{.}{3} @{\qquad} D{.}{.}{3}}
			\toprule
			&     \multicolumn{2}{c}{Men}     &    \multicolumn{2}{c}{Women}    \\
			Estonians:   & \multicolumn{1}{c}{1}   & \multicolumn{1}{l}{\hspace{10pt}2} & \multicolumn{1}{c}{1}   & \multicolumn{1}{c}{2}   \\ \midrule
			Russian     & -0.026^{***}        & -0.001               & -0.009^{*}         & 0.010^{**}         \\
			        & (0.006)          & (0.006)              & (0.005)          & (0.005)          \\
			English     & -0.047^{***}        & -0.019^{***}            & -0.024^{***}        & -0.008^{*}         \\
			        & (0.004)          & (0.005)              & (0.004)          & (0.004)          \\
			\# Observations     & \multicolumn{1}{c}{36,132} & \multicolumn{1}{l}{36,132}     & \multicolumn{1}{l}{36,015} & \multicolumn{1}{c}{36,015} \\
			$R^{2}$     & 0.022           & 0.047               & 0.012           & 0.036           \\ \hline
			Russians: & \\
			Estonian    & -0.052^{***}        & -0.052^{***}            & -0.065^{***}        & -0.045^{***}        \\
			        & (0.010)          & (0.011)              & (0.009)          & (0.010)          \\
			English     & -0.020          & 0.006               & -0.014           & -0.003           \\
			        & (0.012)          & (0.014)              & (0.011)          & (0.012)          \\
			\# Observations     & \multicolumn{1}{c}{12,942} & \multicolumn{1}{l}{12,942}     & \multicolumn{1}{l}{13,674} & \multicolumn{1}{c}{13,674} \\
			$R^{2}$     & 0.033           & 0.066               & 0.023           & 0.043           \\ \hline
			year dummies  & \V             & \V                 & \V             & \V             \\
			indiv. charact. &              & \V                 &              & \V             \\
			\bottomrule
		\end{tabular}
		\begin{flushleft}
			\caption*{ \legend \\ Standard errors (clustered on individuals) in parentheses.\\ Individual characteristics are \modelTwo. \\ \restrictions}
		\end{flushleft}
	\end{center}
\end{table}%

@@

\cref{tab:wage_estimation_by_sex_and_ethnic_same_sample} presents the
central wage regression
results.\footnote{As above, we
restrict both models to have the same number of observations as
requested by a reviewer. The unrestricted table is in the appendix \cref{tab:wage_estimation_by_sex_and_ethnic}.}
The table
confirms the descriptive evidence that wage is positively associated
with fluency in all analysed languages with English showing the
largest effect. The only exception is
Estonian language for Russian men where we fail to find any positive
effect for any of the specifications. This qualitatively repeats the results of
\citet{Toomet2011}. However, for women we observe a sizeable
positive effect between 6 and 16 percentage points, suggesting that
\citet{Toomet2011} results are not valid for the female labour market. The effect decreases somewhat
(from 0.167 to 0.114) when including the individual characteristics
into the model, suggesting that the premium
is partly caused by education and potentially also by unobserved
individual performance. Adding observable workplace characteristics
lowers the effects further to 0.066, suggesting that part of the
language skill premium is realized through workplace selection.

\begin{table}[htbp]
	\begin{center}
		\caption{Estimation results for log wage}
		\label{tab:wage_estimation_by_sex_and_ethnic_same_sample} %SKB 04.07.2018 14:22:Not yet updated only prepared
		%Accounting for occupation in model reduced the Estonian coefficient for women drastically (from 0.12 down 0.06)!
		%For other groups it is less
		\begin{tabular}{l | D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad} | @{\qquad}
				D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad} D{.}{.}{3}}
			\toprule
			&                  \multicolumn{3}{c}{Men}                  &               \multicolumn{3}{c}{Women}                \\
			Estonians     & \multicolumn{1}{c}{\hspace{-12pt}1}   & \multicolumn{1}{l}{\hspace{12pt}2}   & \multicolumn{1}{l}{\hspace{12pt}3} & \multicolumn{1}{c}{\hspace{-12pt}1}   & \multicolumn{1}{l}{\hspace{12pt}2}   & \multicolumn{1}{c}{3}   \\\midrule
			Russian      & 0.112^{***}        & 0.078^{***}        & 0.043^{***}            & 0.094^{***}        & 0.039^{***}        & 0.016^{*}        \\
			          & (0.015)          & (0.015)          & (0.014)              & (0.011)          & (0.011)          & (0.009)          \\
			English      & 0.343^{***}        & 0.158^{***}        & 0.108^{***}            & 0.311^{***}        & 0.130^{***}        & 0.075^{***}        \\
			          & (0.013)          & (0.015)          & (0.013)              & (0.010)          & (0.010)          & (0.009)          \\
			\# Observations       & \multicolumn{1}{l}{21,785} & \multicolumn{1}{l}{21,785} & \multicolumn{1}{l}{21,785}     & \multicolumn{1}{l}{26,673} & \multicolumn{1}{l}{26,644} & \multicolumn{1}{c}{26,449} \\
			$R^{2}$      & 0.730           & 0.760           & 0.801               & 0.769           & 0.810           & 0.830           \\ \midrule
			Russians:     & \\
			Estonian      & 0.020           & -0.013           & -0.009               & 0.167^{***}        & 0.114^{***}        & 0.066^{***}        \\
			          & (0.018)          & (0.019)          & (0.018)              & (0.014)          & (0.014)          & (0.013)          \\
			English      & 0.248^{***}        & 0.152^{***}        & 0.103^{***}            & 0.223^{***}        & 0.089^{***}        & 0.054^{***}        \\
			          & (0.026)          & (0.027)          & (0.024)              & (0.021)          & (0.022)          & (0.018)          \\
			\# Observations       & \multicolumn{1}{l}{7978}  & \multicolumn{1}{l}{7978}  & \multicolumn{1}{l}{7978}      & \multicolumn{1}{l}{9904}  & \multicolumn{1}{l}{9895}  & \multicolumn{1}{c}{9697}  \\
			$R^{2}$      & 0.731           & 0.746           & 0.794               & 0.794           & 0.809           & 0.854           \\ \hline
			year dummies    & \V             & \V             & \V                 & \V             & \V             & \V             \\
			indiv. charact.  &              & \V             & \V                 &              & \V             & \V             \\
			workplace charact. &              &              & \V                 &              &              & \V             \\ \bottomrule
		\end{tabular}
		\begin{flushleft}
			\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis \\ Individual characteristics are \modelTwo. \\ Workplace characteristics are \modelThreeAdd. \\ \restrictions}
		\end{flushleft}
	\end{center}
\end{table}

@@

In conclusion, the wage regressions suggest that English is the
language which is most closely associated with income for men. The effect of Russian language fluency is minor and
that of Estonian language fluency non-existent. For women, all three languages are
associated with higher wage but the Russian language to a smaller extent.
This is in a stark contrast to the unemployment regressions and we return to
this question in the discussion below.

@@

For ethnic Estonians, knowledge of Russian
(Table~\ref{tab:age_group_trend}, upper panel) has become less
important after its peak in the late 1990s. Notably, the
association between wage and language skills are small in the
young groups, the age groups where knowledge of that language
declining rapidly.
For older age groups, the estimates are larger but not statistically
significant since the recession period. English was not important
during the early years of transition but has been very closely
associated with better pay since 1996. Its importance seems to
fall for the young and middle male groups while the oldest men
(45-55) and the youngest women (25-35) show a growing trend.
This potentially reflects both the changing supply and demand for 
English.

Now we turn to ethnic Russians (lower panel in the table). The association between Estonian skills and income shows no
statistically significant results at all. This is the most unexpected
outcome in our analysis and we'll return to this
below in Section~\ref{sec:segregation-analysis}.
The effect of Estonian language skills was initially small for Russian
women as well, but
since the year 2000, we observe a sizeable gain of approximately
10\% for all subgroups.
The positive outcomes for women for the second decade in our analysis
suggests that the previously segregated ``Estonian'' and ``Russian''
economies are slowly becoming a more integrated one where ethnic
Russians, at least women, with good Estonian command get better-paid
jobs than those who cannot speak the language.
In comparison, the estimates for the English language skills trend downward over
time for all age groups for both men and for women. A likely
cause is the increasing abundance of these skills over time.

@@

We document that all analysed language skills are associated with
unemployment and wage, however in a different way. Our most
intriguing observation is that the largest group of
Russian men, high school graduates, earn virtually no income premium if fluent in Estonian,
the majority and the official language of the country, while ability
to speak the language is related to a substantially
lower unemployment rate.
Our analysis supports \citet{YaoandOurs2015}, and \citet{Lindemann2013} findings that 
the labour market is segmented between ethnic and gender lines.
However, we find that ethnic segregation is less prevalent in the male
labour market.
This suggests for the majority of Russian speaking men, Estonian
language gives a distinct advantage by facilitating hiring by
Estonian-dominated employers. But we also confirm
\citet{leppik+vihalemm2015JofBaltStud} conclusion that
these
jobs are associated with little career mobility. There is also some
anecdotal evidence suggesting that offices are
typically manned by ethnic Estonians while manufacturing units have a
large share of Russian workers.
One can speculate that this outcome is related to a substantial population share
with negative attitudes toward Russians \citep{korts2009JofBaltStud}.
On a more positive tone, we find
that this may not be the case for highly educated workers.

@@

\listoffixmes

>>>>

\fxsetup{theme=color}
%Custom commands
\newcommand{\eur}{\EUR}
\newcommand{\std}[1]{\emph{(#1)}}
\newcommand{\V}{\checkmark}
\def\fns{\footnotesize}
\renewcommand*{\vec}[1]{\boldsymbol{#1}}

\def\tenpc{$^{\ast}$}
\def\fivepc{$^{\ast\ast}$}
\def\onepc{$^{\ast\ast\ast}$}
\newcommand{\legend}{\normalsize{Significance levels:\hspace{1em} \tenpc : 10\% \hspace{1em} \fivepc : 5\% \hspace{1em} \onepc : 1\% \normalsize}}
\def\sep{0.5em}
\def\legendTwo{\multicolumn{3}{l}{\footnotesize{Significance levels
			:\hspace{1em} $\dag$ : 10\% \hspace{1em}
			$\ast$ : 5\% \hspace{1em} $\ast\ast$ : 1\% \normalsize}}}
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi} % needed for the tables produced by the esttab command in Stata, to avoid redundancy put here instead of in appendix.tex, where it is needed		
%SKB: Added for documenting the tables and figures
\newcommand{\modelTwo}{age, age\textsuperscript{2}, education, marriage, number of children, inter-ethnic household}
\newcommand{\modelThree}{\modelTwo, industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}
\newcommand{\modelThreeAdd}{industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}	
\newcommand{\restrictions}{The sample period is from year 2000 to year 2012. Sample is limited to persons 25-55 year old.}
\newcommand{\agerestrictions}{25-55 year olds only.}
% Modified section numbering: removed dot at the end as this jumps
% into the cross-references.
\renewcommand{\thesection}{\arabic{section}}
\renewcommand{\thesubsection}{\thesection.\arabic{subsection}}

@@

%\maketitle
%\begin{center}
%	\textbf{{\large Language Skills in an Ethnically Segmented Labour market:
%				Estonia 1989 -- 2012}} \\
%	{\large Sven-Kristjan Bormann} \\
%	\emph{School of Economics and Business Administration, University of Tartu, Narva mnt. 4, 51007 Tartu, Estonia\\ Tel.: +372 5844 3873\\ Email: \href{mailto:bormann@ut.ee}{bormann@ut.ee}}	\\
%
%	{\large Svetlana Ridala} \\
%	\emph{School of Business and Governance, Tallinn University of Technology, Akadeemia tee 3, 12618 Tallinn, Estonia\\ Email: \href{
%			mailto:svetlana.ridala@gmail.com}{
%			svetlana.ridala@gmail.com}} \\
%		{\large Ott Toomet}\\
%		\emph{Information School, University of Washington, USA; Email: \href{mailto:otoomet@uw.edu}{otoomet@uw.edu}}
%%	\emph{(Received XX XXXX 20XX; accepted XX XXXX 20XX)}\\
%	\textbf{Corresponding author:} Sven-Kristjan Bormann Email: \href{mailto:bormann@ut.ee}{bormann@ut.ee}
%\end{center}
%\paragraph{Short biographical note:} \hspace{0pt} \\
%Sven-Kristjan Bormann born 28.11.1985, graduated in 2011 from Kiel University, Germany in Economics with specialisation in Quantitative Economics and Computer Science. Since September 2012 PhD-student in Economics at Tartu University, Estonia. \\
%Svetlana Ridala born 28.03.1976, graduated in 2003 from Tallinn Pedagogical University, Estonia master's (scien) degree in mathematics. Since 2009 PhD-student in Economics at Tallinn School of Economics and Business Administration, Estonia.
%\\
%Ott-Siim Toomet born 18.03.1970, graduated in 2004 from Aarhus University, Denmark PhD in Economics. Since 2015 Visiting scholar, Information School, University of Washington.
%
%\paragraph{Research funding}
%This research was supported by European Social Fund's Doctoral Studies
%and Internationalisation Program DoRa through Archimedes Foundation, and the Estonian Science Foundation grant 8627.
%\newpage
%\noindent
{\centering \textbf{Language Skills in an Ethnically Segmented Labour Market: Estonia 1989 -- 2012}}
\begin{abstract}
 \noindent
 \textbf{Purpose --} We analyse the relationship between skills in the
 Estonian, Russian and English language, and labour market
 outcomes in Estonia, a linguistically divided country.
 \\
 \textbf{Design/methodology/approach --} We use the Estonian Labour
 Force Surveys 1992--2012. We rely on multivariate linear regression
 models to document the relationship between language skills and
 labour market outcomes.
 \\
 \textbf{Findings --} Estonian language knowledge (for ethnic Russians)
 are important determinants of unemployment. Wage, in contrary, is
 closely related to English skills. Ethnic Russian men do not earn
 any premium from speaking Estonian, while women, fluent in Estonian
 earn approximately 10\% more. For ethnic Estonians, Russian fluency
 is associated with a similar income gain.
 \\
 \textbf{Research limitations/implications -- } Due to the
 observational nature of the data, the effects reported in our study
 are not causal effects. As a second limitation, the self-reported
 language skills data may be imprecise and hence the effects we
 report may be too small.
 \\
 \textbf{Practical implications --} Our results stress the role of
 workplace segregation, both along gender and ethnic lines, in
 determining the individual labour market experience. 
 \\
 \textbf{Originality/value --} We provide a comprehensive overview of
 the effects of language skills in a rapidly developing labour
 market in a linguistically divided economy. We analyse several
 languages with different legal status and document long-term
 trends in the effects.
 \\
\end{abstract}
\textbf{Keywords:} language skills, ethnicity, wage gap, unemployment, Estonia \\
\textbf{JEL classification:} J15, J31, J71

@@

We estimate three models that differ in the control variables. The first specification only includes the language skills
and year dummies. It describes the ``raw'' effect of language skills,
net of strong time trends in our data.
The second specification additionally includes individual
characteristics (age, education) and family descriptors (marital
status, an indicator for inter-ethnic marriage, having kids up to 17 years
old) and county of residence. 
Finally, the third specification also adds industry, occupation, and other
workplace descriptors.
Note that for the unemployment probability,
we only estimate the first two models.

@@

\begin{table}[h]
	\begin{center}
		\caption{Estimation results for unemployment.}
		\label{tab:unemployment_estimation_by_sex_and_ethnic_same_sample} %SKB 04.07.2018 14:22:Not yet updated only prepared
		\begin{tabular}{l D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad\qquad}
				D{.}{.}{3} @{\qquad} D{.}{.}{3}}
			\toprule
			&     \multicolumn{2}{c}{Men}     &    \multicolumn{2}{c}{Women}    \\
			Estonians:   & \multicolumn{1}{c}{1}   & \multicolumn{1}{l}{\hspace{10pt}2} & \multicolumn{1}{c}{1}   & \multicolumn{1}{c}{2}   \\ \midrule
			Russian     & -0.026^{***}        & -0.001               & -0.009^{*}         & 0.010^{**}         \\
			        & (0.006)          & (0.006)              & (0.005)          & (0.005)          \\
			English     & -0.047^{***}        & -0.019^{***}            & -0.024^{***}        & -0.008^{*}         \\
			        & (0.004)          & (0.005)              & (0.004)          & (0.004)          \\
			\# Observations     & \multicolumn{1}{c}{36,132} & \multicolumn{1}{l}{36,132}     & \multicolumn{1}{l}{36,015} & \multicolumn{1}{c}{36,015} \\
			$R^{2}$     & 0.022           & 0.047               & 0.012           & 0.036           \\ \hline
			Russians: & \\
			Estonian    & -0.052^{***}        & -0.052^{***}            & -0.065^{***}        & -0.045^{***}        \\
			        & (0.010)          & (0.011)              & (0.009)          & (0.010)          \\
			English     & -0.020          & 0.006               & -0.014           & -0.003           \\
			        & (0.012)          & (0.014)              & (0.011)          & (0.012)          \\
			\# Observations     & \multicolumn{1}{c}{12,942} & \multicolumn{1}{l}{12,942}     & \multicolumn{1}{l}{13,674} & \multicolumn{1}{c}{13,674} \\
			$R^{2}$     & 0.033           & 0.066               & 0.023           & 0.043           \\ \hline
			year dummies  & \V             & \V                 & \V             & \V             \\
			indiv. charact. &              & \V                 &              & \V             \\
			\bottomrule
		\end{tabular}
		\begin{flushleft}
			\caption*{ \legend \\ Standard errors (clustered on individuals) in parentheses; \\  Individual characteristics are \modelTwo.  \restrictions }
		\end{flushleft}
	\end{center}
\end{table}%

@@

\cref{tab:wage_estimation_by_sex_and_ethnic_same_sample} presents the
central wage regression
results.\footnote{As above, we
restrict both models to have the same number of observations as
requested by a reviewer. The unrestricted table is in the appendix \cref{tab:wage_estimation_by_sex_and_ethnic}.}
The table
confirms the descriptive evidence that wage is positively associated
with fluency in all analysed languages with English showing the
largest effect. The only exception is
Estonian language for Russian men where we fail to find any positive
effect for any of the specifications. This finding qualitatively repeats the results of
\citet{Toomet2011}. However, for women we observe a sizeable
positive effect between 6 and 16 percentage points, suggesting that
\citet{Toomet2011} results are not valid for the female labour market. The effect decreases somewhat
(from 0.167 to 0.114) when including the individual characteristics
into the model, suggesting that the premium
is partly caused by education and potentially also by unobserved
individual performance. Adding observable workplace characteristics
lowers the effects further to 0.066, suggesting that part of the
language skill premium is realized through workplace selection.

\begin{table}[htbp]
	\begin{center}
		\caption{Estimation results for log wage}
		\label{tab:wage_estimation_by_sex_and_ethnic_same_sample} %SKB 04.07.2018 14:22:Not yet updated only prepared
		%Accounting for occupation in model reduced the Estonian coefficient for women drastically (from 0.12 down 0.06)!
		%For other groups it is less
		\begin{tabular}{l | D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad} | @{\qquad}
				D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad} D{.}{.}{3}}
			\toprule
			&                  \multicolumn{3}{c}{Men}                  &               \multicolumn{3}{c}{Women}                \\
			Estonians     & \multicolumn{1}{c}{\hspace{-12pt}1}   & \multicolumn{1}{l}{\hspace{12pt}2}   & \multicolumn{1}{l}{\hspace{12pt}3} & \multicolumn{1}{c}{\hspace{-12pt}1}   & \multicolumn{1}{l}{\hspace{12pt}2}   & \multicolumn{1}{c}{3}   \\\midrule
			Russian      & 0.112^{***}        & 0.078^{***}        & 0.043^{***}            & 0.094^{***}        & 0.039^{***}        & 0.016^{*}        \\
			          & (0.015)          & (0.015)          & (0.014)              & (0.011)          & (0.011)          & (0.009)          \\
			English      & 0.343^{***}        & 0.158^{***}        & 0.108^{***}            & 0.311^{***}        & 0.130^{***}        & 0.075^{***}        \\
			          & (0.013)          & (0.015)          & (0.013)              & (0.010)          & (0.010)          & (0.009)          \\
			\# Observations       & \multicolumn{1}{l}{21,785} & \multicolumn{1}{l}{21,785} & \multicolumn{1}{l}{21,785}     & \multicolumn{1}{l}{26,673} & \multicolumn{1}{l}{26,644} & \multicolumn{1}{c}{26,449} \\
			$R^{2}$      & 0.730           & 0.760           & 0.801               & 0.769           & 0.810           & 0.830           \\ \midrule
			Russians:     & \\
			Estonian      & 0.020           & -0.013           & -0.009               & 0.167^{***}        & 0.114^{***}        & 0.066^{***}        \\
			          & (0.018)          & (0.019)          & (0.018)              & (0.014)          & (0.014)          & (0.013)          \\
			English      & 0.248^{***}        & 0.152^{***}        & 0.103^{***}            & 0.223^{***}        & 0.089^{***}        & 0.054^{***}        \\
			          & (0.026)          & (0.027)          & (0.024)              & (0.021)          & (0.022)          & (0.018)          \\
			\# Observations       & \multicolumn{1}{l}{7978}  & \multicolumn{1}{l}{7978}  & \multicolumn{1}{l}{7978}      & \multicolumn{1}{l}{9904}  & \multicolumn{1}{l}{9895}  & \multicolumn{1}{c}{9697}  \\
			$R^{2}$      & 0.731           & 0.746           & 0.794               & 0.794           & 0.809           & 0.854           \\ \hline
			year dummies    & \V             & \V             & \V                 & \V             & \V             & \V             \\
			indiv. charact.  &              & \V             & \V                 &              & \V             & \V             \\
			workplace charact. &              &              & \V                 &              &              & \V             \\ \bottomrule
		\end{tabular}
		\begin{flushleft}
			\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis; \\ Individual characteristics are \modelTwo.  Workplace characteristics are \modelThreeAdd.  \restrictions}
		\end{flushleft}
	\end{center}
\end{table}

@@

In conclusion, the wage regressions suggest that English is the
language which is most closely associated with income for men. The effect of Russian language fluency is minor and
that of Estonian language fluency non-existent. For women, all three languages are
associated with higher wage but the Russian language to a smaller extent.
This result is in a stark contrast to the unemployment regressions and we return to
this question in the discussion below.

@@

For ethnic Estonians, knowledge of Russian
(Table~\ref{tab:age_group_trend}, upper panel) has become less
important after its peak in the late 1990s. Notably, the
association between wage and language skills are small in the
young groups, the age groups where knowledge of that language
declining rapidly.
For older age groups, the estimates are larger but not statistically
significant since the recession period. English was not important
during the early years of transition but has been very closely
associated with better pay since 1996. Its importance seems to
fall for the young and middle male groups while the oldest men
(45-55) and the youngest women (25-35) show a growing trend.
This result potentially reflects both the changing supply and demand for 
English.

Now we turn to ethnic Russians (lower panel in the table). The association between Estonian skills and income shows no
statistically significant results at all. This is the most unexpected
outcome in our analysis, and we'll return to this
below in Section~\ref{sec:segregation-analysis}.
The effect of Estonian language skills was initially small for Russian
women as well, but
since the year 2000, we observe a sizeable gain of approximately
10\% for all subgroups.
The positive outcomes for women for the second decade in our analysis
suggests that the previously segregated ``Estonian'' and ``Russian''
economies are slowly becoming a more integrated one where ethnic
Russians, at least women, with good Estonian command get better-paid
jobs than those who cannot speak the language.
In comparison, the estimates for the English language skills trend downward over
time for all age groups for both men and for women. A likely
cause is the increasing abundance of these skills over time.

@@

We document that all analysed language skills are associated with
unemployment and wage, however in a different way. Our most
intriguing observation is that the largest group of
Russian men, high school graduates, earn virtually no income premium if fluent in Estonian,
the majority and the official language of the country, while ability
to speak the language is related to a substantially
lower unemployment rate.
Our analysis supports \citet{YaoandOurs2015}, and \citet{Lindemann2013} findings that 
the labour market is segmented between ethnic and gender lines.
However, we find that ethnic segregation is less prevalent in the male
labour market.
This suggests for the majority of Russian speaking men, Estonian
language gives a distinct advantage by facilitating hiring by
Estonian-dominated employers. We also confirm
\citet{leppik+vihalemm2015JofBaltStud} conclusion that
these
jobs are associated with little career mobility. There is also some
anecdotal evidence suggesting that offices are
typically manned by ethnic Estonians while manufacturing units have a
large share of Russian workers.
One can speculate that this outcome is related to a substantial population share
with negative attitudes toward Russians \citep{korts2009JofBaltStud}.
On a more positive tone, we find
that this may not be the case for highly educated workers.

@@

%\listoffixmes
